---
title: "Draft Quarto document"
author: "RH"
format: html
---

## Header 1

```{r setup}
library(tidyverse)
library(here)
library(fs)
library(dplyr)
library(stringr)
library(lubridate)
library (tidyselect)
source(here("R/functions.R"))
```


Add to description file all used packages, eg.: usethis::use_package("tidyverse") If you don't know the package name, type in console, eg.: ?read_csv or ?readr or ?here, and find the name in top left corner. Finally, style the code using the Palette (⌃⇧PCtrl-Shift-P, then type “style file”)

#### 'Source' loads the functions into the Quarto document when it is rendered

## Importing new data

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  readr::read_csv(
    show_col_types = FALSE,
    name_repair = snakecase::to_snake_case,
    n_max = 100
  )
```

## Exercise: Reading other files.

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  readr::read_csv(
    show_col_types = FALSE,
    name_repair = snakecase::to_snake_case,
    n_max = 100
  )
```

```{r}
here::here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  readr::read_csv(
    show_col_types = FALSE,
    name_repair = snakecase::to_snake_case,
    n_max = 100
  )
```

```{r}
#' Add two numbers together.
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of the two numbers.
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```

## Import 5C's HR data with a function

```{r}
#| eval: false
#' Read in one nurses' stress data file.
#'
#' @param file_path Path to the data file.
#'
#' @returns Outputs a data frame/tibble.
#'
read <- function(file_path) {
  data <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = 100
    )
  return(data)
}
```

```{r}
#| eval: false
here::here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read()

here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()
```

# Change output n_max to name max_rows

```{r}
#| eval: false
#' Read in one nurses' stress data file.
#'
#' @param file_path Path to the data file.
#' @param max_rows Maximum number of rows to read.
#'
#' @returns Outputs a data frame/tibble.
#'
read <- function(file_path, max_rows = 100) {
  data <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = max_rows
    )
  return(data)
}
```

### Outputs only 1000 rows

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)
```

### Outputs all rows (`Inf` means infinity)

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```


## Using map

The dir_ls() function, which stands for “directory list”, takes the path that we want to search, in this case data-raw/nurses-stress/, an argument to search all sub-folders with recurse = TRUE, and has an argument called regexp to tell it what type of files to search for

```{r}
hr_files <- here("data-raw/nurses-stress/") |>
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)
hr_files
```

All the files are given to map() and all HR files are read into R. list_rbind() to bind (“stack”) the data frames by rows or list_cbind() to bind (“stack”) the data frames by columns. Adding ID information to the data frame as a new column called file_path_id.

```{r}
hr_data <- hr_files |>
  map(read) |>
  list_rbind(names_to = "file_path_id")
hr_data
```

## 18.5 Exercise: Convert map to function and use on sleep.

Type into console: usethis::use_package("fs") and usethis::use_package("purrr") to add to DESCRIPTION

```{r}
#' Read all `.csv.gz` files in the `stress/` folder into one data frame.
#'
#' @param filename The name of files in the sub-folders that we
#'    want to read in.
#'
#' @returns A single data frame/tibble.

read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") |>
    fs::dir_ls(regexp = filename, recurse = TRUE)


  data <- files |>
    purrr::map(read) |>
    purrr::list_rbind(names_to = "file_path_id")

  return(data)
}

read_all("HR.csv.gz")
read_all("IBI.csv.gz")
```

## 19.2 Exercise: Inspecting the data

```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data
```


## 19.6 Using regular expressions to extract text
```{r}
hr_data |>
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/"
    ) |>
      str_remove("/stress/") |>
      str_remove("/"),
    .before = file_path_id
  ) |>
  select(-file_path_id)
```


## 19.7 Exercise: Convert ‘get ID’ code into a function

```{r}
#' Get the participant ID from the file path column. First find string ID including "stress", then remove stress.
#'
#' @param data Data with `file_path_id` column.
#'
#' @returns A data frame/tibble.

get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        pattern = "/stress/[:alnum:]{2}/"
      ) |>
        stringr::str_remove("/stress/") |>
        stringr::str_remove("/"),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)
  return(data_with_id)
}
```


```{r}
#| eval: false
#| include: false

#' Get the participant ID from the file path column. Find string ID without including "stress". ?<= means "preceded by". ?= means "followed by".
#'
#' @param data Data with `file_path_id` column.
#'
#' @returns A data frame/tibble.
get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        "(?<=/stress/)[:alnum:]{2}(?=/)"
      ),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)
  return(data_with_id)
}

get_participant_id(hr_data)
```

## Working with across

```{r}
hr_data <- read_all("HR.csv.gz") |>
  get_participant_id()

hr_data
```


```{r}
hr_data |>
  summarise(
    across(
      where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    )
  )
```


## Working with dates

```{r}
hr_data |>
  mutate(
    datetime = lubridate::round_date(collection_datetime, unit = "minute"),
    .before = collection_datetime
  )
```

## Summarising by groups

```{r}
hr_data |>
  mutate(
    collection_datetime = lubridate::round_date(
      collection_datetime,
      unit = "minute"
    )
  ) |>
  summarise(
    across(
      where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    ),
    .by = c(id, collection_datetime)
  )
```


```{r}
#' Summarise values in a data frame by a rounded datetime
#'
#' @param data A data frame with at least a `collection_datetime` column and
#'  some numeric columns to summarise.
#'
#' @returns A summarised data frame.

summarise_by_datetime <- function(data) {
  summarised_data <- data |>
  dplyr::mutate(
    collection_datetime = lubridate::round_date(
      collection_datetime,
      unit = "minute"
    )
  ) |>
  dplyr::summarise(
    dplyr::across(
      tidyselect::where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    ),
    .by = c(id, collection_datetime)
  ) 
  return(summarised_data)
}

```

## Pivot longer

```{r}
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()
survey_data
```

```{r}
survey_data |>
  mutate(date = mdy(date))
```

```{r}
survey_tidy <- survey_data |>
  mutate(
    date = mdy(date),
    start_datetime = as_datetime(paste(date, start_time)),
    end_datetime = as_datetime(paste(date, end_time)),
    datetime_id = start_datetime,
    .before = start_time
  ) |>
  select(-c(date, start_time, end_time, duration))
```

```{r}
survey_tidy |>
  select(id, datetime_id, start_datetime, end_datetime)
```

