---
title: "Draft Quarto document"
author: "RH"
format: html
---

## Header 1

```{r setup}
library(tidyverse)
library(here)
library(fs)
source(here("R/functions.R"))
```

#### 'Source' loads the functions into the Quarto document when it is rendered


## Importing new data

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  readr::read_csv(
    show_col_types = FALSE,
    name_repair = snakecase::to_snake_case,
    n_max = 100
  )
```

## Exercise: Reading other files.

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  readr::read_csv(
    show_col_types = FALSE,
    name_repair = snakecase::to_snake_case,
    n_max = 100
  )
```

```{r}
here::here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  readr::read_csv(
    show_col_types = FALSE,
    name_repair = snakecase::to_snake_case,
    n_max = 100
  )
```

```{r}
#' Add two numbers together.
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of the two numbers.
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added)
}
```

## Import 5C's HR data with a function

```{r}
#| eval: false
#' Read in one nurses' stress data file.
#'
#' @param file_path Path to the data file.
#'
#' @returns Outputs a data frame/tibble.
#'
read <- function(file_path) {
  data <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = 100
    )
  return(data)
}
```

```{r}
#| eval: false
here::here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read()

here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()
```


# Change output n_max to name max_rows
```{r}
#| eval: false
#' Read in one nurses' stress data file.
#'
#' @param file_path Path to the data file.
#' @param max_rows Maximum number of rows to read.
#'
#' @returns Outputs a data frame/tibble.
#'
read <- function(file_path, max_rows = 100) {
  data <- file_path |>
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = max_rows
    )
  return(data)
}
```

### Outputs only 1000 rows

```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)
```

### Outputs all rows (`Inf` means infinity)
```{r}
here::here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```


Add to description file all used packages, eg.: usethis::use_package("tidyverse")
If you don't know the package name, type in console, eg.: ?read_csv or ?readr or ?here, and find the name in top left corner.
Finally, style the code using the Palette (⌃⇧PCtrl-Shift-P, then type “style file”)



## Using map

The dir_ls() function, which stands for “directory list”, takes the path that we want to search, in this case data-raw/nurses-stress/, an argument to search all sub-folders with recurse = TRUE, and has an argument called regexp to tell it what type of files to search for

```{r}
hr_files <- here("data-raw/nurses-stress/") |>
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE)

hr_files
```

All the files are given to map() and all HR files are read into R.
list_rbind() to bind (“stack”) the data frames by rows or list_cbind() to bind (“stack”) the data frames by columns.
Adding ID information to the data frame as a new column called file_path_id.
```{r}
hr_data <- hr_files |>
  map(read) |>
  list_rbind(names_to = "file_path_id")
hr_data
```
